### 2017-11-27 Risk analysis/Text/Layout/Layout/MSc_layout_Fabian.tex
Cleaning Notebooks2
Formatting

\documentclass[a4paper,11pt]{MScThesis}
%
%\usepackage{pifont}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{booktabs}
\graphicspath{Figures/}
%\usepackage{mathpazo}
\mscName{Fabian Antonio Stamm}
\mscDate{\today}
\mscTitle{Bayesian Decision Theory in Structural Geological Modeling}
\mscSubTitle{How Reducing Uncertainties Affects Reservoir Value Estimations}
\mscKeyWords{thesis, msc, subject}
%
%\mscBackPicture{2660PF3}    % eps of 21 * 29.7 cm
\mscReaderOne{Prof. Florian Wellmann, Ph.D.}
\mscReaderTwo{Prof. Dr. Janos Urai}
\mscReaderThree{Miguel de la Varga, M.Sc.}
%\mscReaderFour{}
%
\setThesisInfo
%
\begin{document}
%
%============================= Front matter ========================================
\frontmatter %
%
% Make a hell of a lot of title pages
    \maketitle
%
% Abstract
	\nonumchap{Abstract}
Bayesian decision theory is applicable to a wide spectrum of problems. Hydrocarbon exploration and production is a high-risk, high-reward sector in which good decision making is indispensable. Actors in this field are faced by numerous uncertainties that have to be considered. Structural geological modeling is of central importance for the assessment of uncertain hydrocarbon accumulations in potential reservoirs. By regarding such modeling as a Bayesian inference problem, additional geological information can be incorporated as likelihood functions linked to prior parameters in a probabilistic framework. Markov chain Monte Carlo sampling is used to approximate posterior models of reduced uncertainty. Here, synthetic geological models are constructed to represent potential hydrocarbon system. Algorithms for automatic trap recognition are developed to enable the reservoir valuation of prior and posterior models. These serve as a base for true value estimation by respective optimization of a case-specific loss function. This function is customized to reflect the decision making of differently risk-affine actors in this context. Results from conducting this for several inference cases show that the various Bayes estimators shift according to the characteristics of the underlying value distribution. While bimodality and overall uncertainty leads to separation, risk-averse and risk-friendly decisions converge and decrease in expected loss. These degree of these processes is considered a measure for the state of knowledge and decision uncertainty at the decision-making moment. This decision uncertainty does not change aligned with model uncertainty, but depends on alterations of critical parameter and interdependencies, relating to seal reliability in particular. Additionally, actors affected differently by one set of information, as defined by their risk-opportunity weighting. For good decision making, it appears to be most important to recognize in for which parameters reduction of uncertainty leads to changes in decisions.

@@

%
% table of contents, (\toc or \toclof or \tocloflot )
    \tocloflot
%
% Nomenclature
    \printnomencl %
%
% Acronyms
    \nonumchap{Acronyms} %
    %
    \begin{acronym}%
        \acro{RWTH}{Aachen University}%
    \end{acronym}%
    %
    \cleardoublepage%
%
%
%============================= Main matter =========================================
%
\mainmatter
%
% Introduction
%\include{chapter1} % notice how the reference to the introduction takes place.. It refers to the name.tex

@@

    \chapter{The back of the thesis}

    \section{An appendix section}

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.62\textwidth]{Figures/Appendix/CSV_input1}
    	\caption{....}\label{fig:CSV_input1}
    \end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.62\textwidth]{Figures/Appendix/CSV_input2}
		\caption{....}\label{fig:CSV_input2}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=1\textwidth]{Figures/Appendix/CSV_input3}
		\caption{....}\label{fig:CSV_input3}
	\end{figure}

    \begin{figure}[p!]
    	\centering
    	\includegraphics[width=1\textwidth]{Figures/Appendix/ML3}
    	\caption{....}\label{fig:ML3}
    \end{figure}

    \subsection{An appendix subsection with C++ Lisitng}

    \lstset{language=C++}
    \lstinputlisting{test.c}

    \subsection{A \matlab $ $ Listing}

    \lstset{language=matlab}
    \lstinputlisting{test.m}

    \chapter{Yet another appendix}

    \section{Another test section}

    Ok, all is well.

>>>>

\documentclass[a4paper,11pt]{MScThesis}
%
%\usepackage{pifont}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage{booktabs}
\graphicspath{Figures/}
%\usepackage{mathpazo}
\mscName{Fabian Antonio Stamm}
\mscDate{\today}
\mscTitle{Bayesian Decision Theory in Structural Geological Modeling}
\mscSubTitle{How Reducing Uncertainties Affects Reservoir Value Estimations}
\mscKeyWords{thesis, msc, subject}
%
%\mscBackPicture{2660PF3}    % eps of 21 * 29.7 cm
\mscReaderOne{Prof. Florian Wellmann, Ph.D.}
\mscReaderTwo{Prof. Dr. Janos Urai}
\mscReaderThree{Miguel de la Varga, M.Sc.}
%\mscReaderFour{}
%
\setThesisInfo
%
\begin{document}
%
%============================= Front matter ========================================
\frontmatter %
%
% Make a hell of a lot of title pages
    \maketitle
%
Statutory Declaration in Lieu of an Oath

\vspace*{0.1\textheight}

\noindent\begin{minipage}[t]{0.5\textwidth}
\begin{flushleft} \large

%\authorname \\
Stamm, Fabian \\
\emph{\footnotesize Last Name, First Name}

\end{flushleft}
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\begin{flushright} \large

%123456 \\
%\emph{\footnotesize Matriculation No.}

\end{flushright}
\end{minipage}\\[1cm]

\noindent I hereby declare in lieu of an oath that I have completed the present Master thesis entitled "\msctitle\ - \mscsubtitle" independently and without illegitimate assistance from third parties. I have used no other than the specified sources and aids. In case that the thesis is additionally submitted in an electronic format, I declare that the written and electronic versions are fully identical. The thesis has not been submitted to any examination body in this, or similar, form.\\[2cm]

\noindent\begin{minipage}[t]{0.5\textwidth}
\begin{flushleft} \large

Aachen, \today \\
\emph{\footnotesize City, Date}

\end{flushleft}
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\begin{flushright} \large

\break
\rule{10em}{0.5pt}\\ % This prints a line for the signature
\emph{\footnotesize Signature}

\end{flushright}
\end{minipage}\\[3cm]

\cleardoublepage

% Abstract
\nonumchap{Abstract}
Bayesian decision theory is applicable to a wide spectrum of problems. Hydrocarbon exploration and production is a high-risk, high-reward sector in which good decision making is indispensable. Actors in this field are faced by numerous uncertainties that have to be considered. Structural geological modeling is of central importance for the assessment of uncertain hydrocarbon accumulations in potential reservoirs. By regarding such modeling as a Bayesian inference problem, additional geological information can be incorporated as likelihood functions linked to prior parameters in a probabilistic framework. Markov chain Monte Carlo sampling is used to approximate posterior models of reduced uncertainty. Here, synthetic geological models are constructed to represent potential hydrocarbon system. Algorithms for automatic trap recognition are developed to enable the reservoir valuation of prior and posterior models. These serve as a base for true value estimation by respective optimization of a case-specific loss function. This function is customized to reflect the decision making of differently risk-affine actors in this context. Results from conducting this for several inference cases show that the various Bayes estimators shift according to the characteristics of the underlying value distribution. While bimodality and overall uncertainty leads to separation, risk-averse and risk-friendly decisions converge and decrease in expected loss given more narrow unimodal distributions. The degree of decision convergence is considered a measure for the state of knowledge and decision uncertainty at the moment of decision making. This decision uncertainty does not change aligned with model uncertainty but depends on alterations of critical parameters and respective interdependencies, relating to seal reliability in particular. Additionally, actors are affected differently by one set of information, as defined by their risk weighting. For good decision making, it appears to be most important to recognize for which parameters reduction of uncertainty leads to changes in decisions.

@@

%
% table of contents, (\toc or \toclof or \tocloflot )
    \tocloflot
%
% Nomenclature
    %\printnomencl %
%
% Acronyms
    \nonumchap{Acronyms} %
    %
    \begin{acronym}%
    	\acro{CSV}{Comma-separated values}%
    	\acro{MAP}{Maximum a posteriori}%
        \acro{MCMC}{Markov chain Monte Carlo}
        \acro{NPV}{Net present value}%
        \acro{OOIP}{Original oil-in-place}
        \acro{ROV}{Recoverable oil volumes}%
        \acro{SSF}{Shale Smear Factor}
    \end{acronym}%
    %
    \cleardoublepage%
%
%
%============================= Main matter =========================================
%
\mainmatter
%
% Introduction
%\include{chapter1} % notice how the reference to the introduction takes place.. It refers to the name.tex

@@

    \chapter{Appendix}
    \section{Code availability}
    	GemPy and PyMC are both fully open source and to be used in a Python environment. At the time of writing this, GemPy is still under development (Version 0.997). It can be obtained from \url{https://github.com/cgre-aachen/gempy}. PyMC can be downloaded from \url{https://github.com/pymc-devs/pymc} (PyMC2) and \url{https://github.com/pymc-devs/pymc3} (PyMC3).\\
    	The models, algorithms and functions developed and presented in this work can be found on \url{https://github.com/nre-aachen/Theses/tree/master/Risk analysis}.

    \section{Additional tables and figures}

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.62\textwidth]{Figures/Appendix/update_goodseal1}
    	\caption{Prior (A1) and posterior distributions (B1) of the layer boundary positions in depth and respective representations (A2, B2) for 1D inference case II.}\label{fig:update_goodseal1}
    \end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.62\textwidth]{Figures/Appendix/update_smallres1}
		\caption{Prior (A1) and posterior distributions (B1) of the layer boundary positions in depth and respective representations (A2, B2) for 1D inference case III.}\label{fig:update_smallres1}
	\end{figure}

    \begin{figure}[h]
    	\centering
    	\includegraphics[width=0.62\textwidth]{Figures/Appendix/CSV_input1}
    	\caption{3D model construction input data 1: point-positional values for layer interfaces and the fault surface.}\label{fig:CSV_input1}
    \end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.62\textwidth]{Figures/Appendix/CSV_input2}
		\caption{3D model construction input data 2: point-positional values for layer interfaces and the fault surface.}\label{fig:CSV_input2}
	\end{figure}

	\begin{figure}[h]
		\centering
		\includegraphics[width=1\textwidth]{Figures/Appendix/CSV_input3}
		\caption{3D model construction input data 3: dip -related values for layer interfaces and the fault surface.}\label{fig:CSV_input3}
	\end{figure}

    \begin{figure}[p!]
    	\centering
    	\includegraphics[width=1\textwidth]{Figures/Appendix/ML3}
    	\caption{Summary of results from evaluating posterior model II (3D). Shannon entropies in prior (a) and posterior (b) are compared. So are the mechanisms of maximum trap volume control (c). Prior and posterior ROV probability distributions are shown in (d). Respective loss function and Bayes actions are plotted in (e).}\label{fig:ML3}
    \end{figure}

    %\section{Another test section}

    %Ok, all is well.
